\documentclass{assets/syllabus}
\begin{document}

% Output the header for the course syllabus document:
\Heading

% Do not introduce any blank lines betweeen these brackets.
\Coursehead[
% The following defines the data fields used in the document:
%
% INSTRUCTOR INFORMATION
instructor      = {Daniel Cicala},
phone           = {},
email           = {dcicala@newhaven.edu},
webpages        = {https://danielmichaelcicala.github.io/teaching},
%
% COURSE TEXT AND SYLLABUS
course          = {MATH 1117},
coursesection   = {-\,05}, % We use the - style to denote course sections.
coursetext      = {\textit{Calculus: Early Transcendentals}, by Briggs, Cochran, Gillett,  Pearson, 3e, ISBN 978-0-13-476364-45},
coursecrosslist = {},
coursename      = {Calculus I},
credits         = {4},
%
% COURSE TIME AND LOCATION
revision        = {},
semester        = {Spring 2020},
office          = {Maxcy 323},
meetingtimes    = {MWF 10:50am--12:05pm},
classroom       = {KAPL 203},
officehours     = {MW 9--10am \& 1pm--2pm // F 1--3pm},
addanddrop           = {W 29 Jan 2020},
%semesterclasses      = {Spring Semester 2016},
startsemesterclasses = {W 22 Jan 2020},
endsemesterclasses   = {W 13 May 2020},
lastdropdate         = {T 24 Mar 2020},
%semesterholidays     = {Memorial Day Monday, May 29},
semesterfinalexam    = {T 12 May 2020}
]

\syllabusfontn
\Title{$\S$\,II: Instructors Addendum}
\SubTitle{For \Course\Coursesection \Coursename}
\vspace*{0.8em}

% ===========================================
% DISCLAIMER THAT I CAN AMEND SYLLABUS
% ===========================================

\Subtopic{Disclaimer}

I reserve the right to make changes to this
syllabus. All changes will be announced in a
timely manner through email or classroom
announcements.

% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\Subtopic{Department Syllabus} This is the
instructor portion of the syllabus.  see the
department syllabus, located at
\begin{center} \href{https://danielmichaelcicala.github.io/teaching/syl_dept_cal.pdf}{https://danielmichaelcicala.github.io/teaching/syl_dept_cal.pdf}
\end{center}
for department policies and resources.  

% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\Subtopic{Required Textbook}

\Coursetext.

% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\Subtopic{Course Website}

I will only use Blackboard to email the class and
to make announcements.  Be sure that you have
emails from Blackboard whitelisted. All other
course information is on the course website
\href{https://danielmichaelcicala.github.io/teaching}{listed
  above.}.  In particular, I will not post grades
on Blackboard, but I am always happy to discuss
your grade in-person during office hours.

% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\Subtopic{Worksheets}

During each lecture, students will complete a
worksheet to be handed in at the end of class.  It
will be graded for completeness, not correctness. 

Worksheets are worth 10\% of your total grade.

% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\Subtopic{Homework}

On my website listed above, you will find a number
of homework problems and their due date. They are
to be handed in to me or placed in the folder
outside my office by 4pm on the due date. Late
assignments will not be accepted without a
university approved reason. Assignments that are
not stapled or without names will not receive
credit.

Each homework will be given a score between 0 and
10 that corresponds with the percentage of the
assignment you completed. For a question to count
as ``complete'', you must either have provided a
full, though not necessarily correct, answer. In
lieu of a full answer, you can either (1) discuss
the question with me in my office hours prior to
the due date of the related assignment, or (2)
write a short paragraph that examines exactly why
you had difficulty and what you tried to do when
you got stuck.

Calculus is a *skill* that can be developed and
like all skills, it requires practice.  It is
impossible to get better without making and
learning from mistakes.  By developing the ability
to recognize your mistakes, then soon enough you
will catch them in real-time and prevent making
them all together. This homework is to allow you
to be wrong while not hurting your grade.  I will
offer vague comments to direct your attention to
areas of your work where I think you can do
better. You should study these areas to better
understand them. I encourage you to come to office
hours to discuss any of my comments.

Homework contributes 15\% of your total grade.


% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\Subtopic{Quizzes}

On each day when a homework is due, there will be
a short quiz. This quiz will consist of questions
pulled *directly* from the assigned homework. You
may not use your text, notes, or any
electronics. Each question, graded for correctness
and clarity, will be given a score between 0 and
10.

These quizzes are to practice your ability to
recall mathematical information. This
ability---which, again, is a skill to be
developed---serves as a frame onto which new
knowledge is built.  Also, to solve a problem,
recall is needed for you to sythesize the
information into a solution.  You cannot
synthesize information held in a second-brain,
e.g.~a notebook or the internet. Quizzes are a
low-stakes way for you to practice your ability to
access information.

Quizzes are worth 15\% of your total grade.

% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\Subtopic{Exams}

There are two exams during the semester and one
final exam. All exams are closed notes and closed
books. Calculators and other electronics are also
not allowed. Any attempt to cheat will be dealt
with according to the misconduct code.  Students
found to have violated the rules governing
academic integrity will receive a 0 grade on the
associated exam and may be subject to further
penalties as allowed by the University.

Not only are exams meant to measure the breadth of
knowledge you've obtained, but they are actually
an important part of *enhancing* your knowledge.

Each midterm exam contributes 15\% your total
grade.  The final exam contributes 30\% of the
total grade.


% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\Subtopic{Scoring and Course Grades}

The letter grade is based on the student's total
point score for the semester.  The class letter
grade is assigned based on

% table assigning point grade to letter grade
\begin{center}
	
\syllabusfonts
\renewcommand{\arraystretch}{1.20}
\renewcommand{\colorfirst}{paleblue1}
\rowcolors{2}{\colorfirst}{white}
\begin{center}
  \begin{tabular}{|l|l|}
    \hline
    \textbf{Points} & \textbf{Grade} \\
    \hline
    97.5--100.0 & \hspace*{0.8em} \ec A\,+  \\
    92.5--97.5  & \hspace*{0.8em} \ec A     \\
    90.0--92.5  & \hspace*{0.8em} \ec A\;-- \\
    87.5--90.0  & \hspace*{0.8em} \ec B\,+  \\
    82.5--87.5  & \hspace*{0.8em} \ec B     \\
    80.0--82.5  & \hspace*{0.8em} \ec B\;-- \\
    \hline
  \end{tabular} \hspace*{1.8em}
  \rowcolors{2}{\colorfirst}{white}
  \begin{tabular}{|l|l|}
    \hline
    \textbf{Points} & \textbf{Grade} \\
    \hline
    77.5--80.0 & \hspace*{0.8em} \ec C\,+   \\
    72.5--77.5 & \hspace*{0.8em} \ec C      \\
    70.0--72.5 & \hspace*{0.8em} \ec C\;--  \\
    67.5--70.0 & \hspace*{0.8em} \ec D\,+   \\
    62.5--67.5 & \hspace*{0.8em} \ec D      \\
    60.0--62.5 & \hspace*{0.8em} \ec D-     \\
    0--60      & \hspace*{0.8em} \ec F      \\
    \hline
  \end{tabular}
  
\end{center}
\syllabusfontn
	
\end{center}

% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\Subtopic{Grade Calculation}

The total grade will be calculated using the formula
\[
  0.10 (\textrm{class part.}) +
  0.15 (\textrm{hw}) +
  0.15 (\textrm{quizzes}) +
  0.30 (\textrm{midterm exams}) +
  0.30 (\textrm{final exam})
\]

% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\Subtopic{Course Outline Schedule}

\Semester\ classes are from \Startsemesterclasses\
to \Endsemesterclasses.  The last day to drop
classes without any financial penalty is
\Addanddrop, and the last day to withdraw from the
class, i.e., to request a {\ec W} grade is prior
to \Lastdropdate.  All requests for a W must be
sent to the registrar.

The following is a tentative schedule. The exam dates are
also noted on the schedule. These dates are subject to
change; this includes the exams.

\begin{center}
  \rowcolors{2}{cyan!15}{white}
  \begin{tabular}{|l l|}
    \hline
    \rowcolor{cyan!30}{\textbf{Dates}} & \textbf{Section} \\ 
    \hline
    {\bf Week 1}  & 1.1, 1.2, 1.3, 1.4 \\
    {\bf Week 2}  & 2.1, 2.2, 2.3, 2.4 \\
    {\bf Week 3}  & 2.4, 2.5, 2.6 \\
    {\bf Week 4}  & 3.1, 3.2 \\
    {\bf Week 5}  & 3.3, 3.4, 3.5 \\
    {\bf Week 6}  & 3.6, 3.7, \emph{exam 1} \\
    {\bf Week 7}  & 3.8, 3.9, 3.10 \\
    {\bf Week 8}  & 3.11 \\
    {\bf Week 9}  & 4.1, 4.2, 4.3 \\
    {\bf Week 10} & 4.4, 4.5 \\
    {\bf Week 11} & 4.6, 4.7, 4.8 \\
    {\bf Week 12} & 4.9, \emph{exam 2} \\
    {\bf Week 13} & 5.1, 5.2 \\
    {\bf Week 14} & 5.3, 5.4, 5.5 \\
    \hline
    {\bf Final Exam} & \Semesterfinalexam \\
    \hline
  \end{tabular}
\end{center}


%COPIES OF THE SCHEDULE FOR MW AND TR ARE KEPT IN ./lib.........................
{
\renewcommand{\syllabusfontstable}{\syllabusfontf}
\renewcommand{\tableheader}{\tableheaders}
%\input{schedule.tex}
}

\LastPage

\end{document}

