% PACKAGES AND OTHER DOCUMENT CONFIGURATIONS

\documentclass{Resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{verbatim}
\usepackage{multicol}

\name{Daniel Cicala} % Your name
\address{Department of Mathematics \\ University of California, Riverside} 
\address{danielmichaelcicala.github.io} 

\begin{document}

%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%
%	EDUCATION SECTION
%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%

\begin{rSection}{Education}

{\sc University of California, Riverside} 
\hfill 
{2019} \\ 
\textit{Ph.D. in Mathematics} 
\hfill 
{\em Riverside, California} \\
Supervisor: Dr. John Baez \\
Thesis: Rewriting open cospans: a syntax for open systems

{\sc University of Ottawa} 
\hfill 
{2014} \\ 
\textit{Masters of Science in Mathematics}
\hfill
{\em Ottawa, Ontario} \\
Co-supervisors: Dr. Richard Blute and Dr. Alistair Savage \\
Thesis: {Matrix Problems and their Relation to the Representation Theory of Quivers and Posets }

{\sc New Jersey Institute of Technology} 
\hfill 
{2008} \\ 
\textit{Bachelor of Science in Mathematics} 
\hfill
{\em Newark, New Jersey}

\end{rSection}





%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%
%	PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%

\begin{rSection}{Publications \& Preprints}

  \textbf{Published}
  
  Categorifying the ZX-calculus.  \emph{Proceedings 14th International
    Conference on Quantum Physics and Logic}, 294--314,
  Electron. Proc. Theor. Comput. Sci. (EPTCS), 266, EPTCS, 2018.
  
  (with Kenny Courser) Spans of cospans in a topos. \emph{Theory
    Appl. Categ.}, Vol. 33, No. 1, pp 1-22. 2018
	
  Spans of cospans.  \emph{Theory Appl. Categ.}, Vol. 33, 2018, No. 6,
  pp 131-147.

  \textbf{In preparation}
  
  Inductive rewriting for compositional models of abstract
  networks.
  
\end{rSection}





%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%
%	TALKS
%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%

\begin{rSection}{Talks}

  \textsc{Borsuk-Ulam in real-cohesive homotopy type theory} \hfill
  (Carnegie Mellon, August 2019) \\
  International Conference on Homotopy Type Theory
  
  \textsc{Rewriting structured cospans} \hfill
  (Chapman University, May 2019) \\
  Symposium on Compositional Structures 4

   \textsc{Global Cascades on Social Networks} \hfill
  (Riverside, Jan.~2019) \\
  UC Riverside Network Theory Seminar
  
    \textsc{Syntax and inductive rewriting for open networks} \hfill
  (Baltimore, Jan.~2019) \\
  Joint Mathematics Meetings, special session in Network Science

  \textsc{A categorical syntax with structural rewriting for networks} \hfill
  (Scripps, Oct.~2018) \\
  SoCal-Nevada MAA Section
  
  \textsc{A low-key introduction to synthetic differential geometry} \hfill
  (UC Riverside, May.~2018) \\
  Math Connections
  
  \textsc{A  syntax for pure state qubit quantum mechanics} \hfill (UC Riverside, Nov.~2017) \\
  AMS Western Sectional

  \textsc{Open graphs in bicategories of spans and cospans} \hfill
  (U.~British Columbia, July 2017) \\
  Category Theory 2017
	
  \textsc{Generalizing Lawvere theories} \hfill
  (U.~British Columbia, July 2017) \\
  Category Theory 2017
	
  \textsc{Categorifying the ZX-calculus} \hfill
  (Radboud University, July 2017) \\
  Quantum Physics \& Logic 2017

  \textsc{Universal algebra and functorial semantics} \hfill
  (UC Riverside, April 2017) \\
  UCR Graduate Student Seminar
	
  \textsc{Notions of Lawvere theories} \hfill
  (Virtual, April 2017) \\
  Kan Extension II
	
  \textsc{Span of cospans} \hfill
  (UC Riverside, Sept.~2016) \\
  UCR Graduate Student Seminar

  \textsc{Quasi-categories} \hfill
  (UC Riverside, Febr.~2016) \\
  Dr.\ Julie Bergner's Homotopy Theory Seminar
\end{rSection}





%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%
% TEACHING EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%

\begin{rSection}{Professional Experience}

\textbf{Instructor of Record}
  
  \textsc{University of California, Riverside} 
  \\
  Multi-variable calculus; Machine learning (undergraduate
  research project); Topology Ph.D.~qualifying exam seminar
  
  \textsc{Riverside City College} \\
  Statistics; Precalculus; Intermediate Algebra

  \textsc{Mt.~San Jacinto College} \\
  Precalculus; Intermediate Algebra

  \textsc{City College of New York} \\
  Precalculus

\textbf{Teaching Assistant} 

  \textsc{University of California, Riverside} \\
  College Mathematics; Precalculus; Calculus I, II, \& III;
  Differential Equations; (computational) Linear Algebra;
  (proof-based) Linear Algebra; Introduction to Topology;
  Intermediate Analysis; Multi-variable Calculus; Mathematical Modeling

  \textsc{University of Ottawa}  \\
  Functions; Calculus I, II, \& III; Introduction to Analysis; Introduction to Linear Algebra

\textbf{Other}

  \textsc{Rchain/Pyrofex} (May 2018 -- current) \\
  Making precise and writing on process calculi and category theory
  relevant to blockchain technology.

  \textsc{Insurances Service Office} (2008 -- 2009) \\
  Junior level actuary

\end{rSection}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% OTHER PROFESSIONAL SERIVE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{rSection}{Professional Service}

  {\sc Applied Category Theory 2019}
  \hfill
  Spring 2019 \\
  {\em Oxford University} \\
  I am organizing a workshop for 20 grad students and 5 professional
  researchers. There is a five month online portion for students to
  gain background by presenting papers assigned by the researchers
  followed by a one week in-person workshop at Oxford University to
  prove conjectures made by the researchers.

  {\sc Article Reviewer} \\
  {\em AMS} \\
  Write article reviews for the the AMS's Mathematical Reviews
  (MR) Database.  

  {\sc Mathematics Graduate Student Association} \\
  {\em UC Riverside} \\
  Formed a chapter of the UCR Graduate Student Union and served as
  president for its first year.
  
\end{rSection}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%	PROFESSIONAL DEVELOPMENT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{rSection}{Professional Development}

  {\sc Second Statebox Summit 2018} \hfill
  {September 2018} \\
  \hfill
  {\em Schoorl, Netherlands} \\
  Summit organized by Statebox to advance mathematical methods useful
  in blockchain technology.
  
  {\sc Applied Category Theory 2018} \hfill
  {Spring 2018} \\
  \hfill
  {\em Leiden, Netherlands} \\
  Workshop organized by Bob Coecke, Brendan Fong, Aleks Kissinger,
  Martha Lewis, Joshua Tan.
	
  {\sc Kan Extension Seminar} \hfill
  {Spring 2017} \\
  \hfill
  {\em Worldwide via video calls} \\
  Seminar organized by Emily Riehl, Brendan Fong, and Alexander
  Campbell.
	
  {\sc MRC in Homotopy Type Theory} \hfill
  {Summer 2017} \\
  \hfill
  {\em Snowbird, Utah} \\
  Working group led by Mike Shulman and Dan Licata focused on
  applications of cohesive HoTT.
        
  {\sc AARMS} \hfill
  {Summer 2016} \\
  \hfill
  {\em Halifax, Nova Scotia} \\
  Courses: \\
  $ \bullet $ {Categorical Logic and Higher Category Theory by
    Mike Shulman and Peter Lumsdaine} \\
  $ \bullet $ {Categories, Quantum Computation, and Topology by Jamie
    Vicary}
		
\end{rSection}


%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%
%	PROFESSIONAL EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%

%\begin{rSection}{Professional Experience}
%
%-------------------------------
%
%\begin{rSubsection}{Insurance Analyst}{2008-2010}{Insurance Services Office}{Jersey City, NJ}
%	\item Compiled and edited documents investigating expected \textit{loss costs} for various lines of insurance.
%	\item Communicated relevant changes and updates in state insurance laws to insurance companies. 
%\end{rSubsection}
%
%-------------------------
%
%\end{rSection}

%
%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%
%%	ADDITIONAL ACTIVITY
%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%
%
%\begin{rSection}{Additional Activity and Memberships}
%
%
%\textbf{Math Graduate Student Association -- President \& Co-founder} \hfill {2014-2016} \\ \textit{University of California, Riverside}
%
%
%\textbf{Graduate Student Union -- Member} \hfill 2014 \\ \textit{University of California, Riverside} 
%
%\textbf{American Mathematical Society -- Member} \hfill Since 2012 
%
%\textbf{Pi Mu Epsilon -- Member} \hfill Since 2007 
%
%\end{rSection}

%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%
% AWARDS AND HONOURS
%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%

\begin{rSection}{Awards and Honors}

\textbf{Dissertation Year Fellowship} \hfill 2018 \\ \textit{University of California, Riverside}
  
\textbf{Early Promise in the Graduate Career Prize} \hfill 2015 \\ \textit{University of California, Riverside} 

\textbf{Chancellor's Distinguished Fellowship} \hfill 2014 \\ \textit{University of California, Riverside} 

\textbf{Magna Cum Laude} \hfill 2008 \\ \textit{New Jersey Institute of Technology} 

\end{rSection}


%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%
%  END DOCUMENT
%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%

\end{document}
